Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2016-03-08 draft.tex
add new restriction to cover case where s prefers war to ceding

\item \textit{For both players $g$ and $s$, $\frac {Q_i^0}{1-\delta} \geq  -\zeta_i+\frac{W_i^0(p_i) + L_i^0(1-p_i)}{1-\delta}$: the expected outcome under war is worse than the status quo at the beginning of the game.}\label{res:2}

>>>>

\item \textit{For both players $g$ and $s$, $\frac {Q_i^0}{1-\delta} \geq \frac {\omega_i^0}{1-\delta} = -\zeta_i+\frac{W_i^0(p_i) + L_i^0(1-p_i)}{1-\delta}$: the expected outcome under war is worse than the status quo at the beginning of the game.}\label{res:2}

\item \textit{Either (a) $\frac{L_s^0}{1-\delta}  > \frac{\omega_s^0}{1-\delta}$ or (b) $0 > \frac{\lambda p_s - \alpha (1-p_s)}{1-\de} > -\mu$: either the secessionists prefer ceding to war or the patron's disutility from war is greater than the per-period cost of offsetting the deterioration in the secessionists' status quo payoffs.}\label{res:new}
